\racets: Policy{-}Agnostic Programming in Racket

### 2018-07-24 paper/paper.tex

The advantage of this approach is that faceted, policy-agnostic, programs may be written
directly in Racket, making use of the wealth of Racket code already available.
A central challenge of this then, is how to ensure there is a sound and practical inter-operation
between racets and standard Racket (or other languages written as libraries in Racket). Our
approach to this has been to use a tagging scheme that identifies values from \racets
so untagged values may be treated by \racets as originating from a non-\racets language.
For example, a pure Racket function that is not tagged, being applied at a $\blue{\code{ppapp}}$
form in \racets, can be automatically lifted to support FE (so that it can split when applied
on a faceted value).

>>>>

The advantage of this approach is that faceted, policy-agnostic, programs may be written
directly in Racket, making use of the wealth of Racket code already available.
A central challenge of this then, is how to ensure there is a sound (w.r.t. secure multi-execution)
and practical inter-operation between \racets and standard Racket (or other languages written as
libraries in Racket). Our approach to this has been to use a tagging scheme that identifies values
from \racets so untagged values may be treated by \racets as originating from a non-\racets language.
For example, a pure Racket function that is not tagged, being applied at a $\blue{\code{ppapp}}$
form in \racets, can be automatically lifted to support FE (so that it can split when applied
on a faceted value).
